---
title: "Discussion of Matching Mechanisms and Justified Envy: Stability on the Intensive Margin"
subtitle: "Le Kang, Wei Ha, Yang Song, Sen Zhou"
author: "Discussant: Eren Bilen, Assistant Professor of <br> Data Analytics"
institute: "Dickinson College"
date: "The Chinese Economists Society North America Conference, Lewisburg, PA"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    includes:
      after_body: insert-logo.html
editor_options: 
  chunk_output_type: console
---

<style>
.caption {
  text-align: center;
  font-size: 14px;
}
</style>

<!--
.caption:before {
  content:"Figure: ";
  font-weight: bold;
} -->

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_light(base_color = "#23395b")
```

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r,echo=F}
#library(countdown)
#countdown(minutes = 0, seconds = 10, top = 2,left = 5, right = 5)
```

**Research question:**
- Did the switch from Immediate Acceptance matching to Parallel <br> mechanism (a version of Deferred Acceptance algo.) improve "justified <br> envy" in CEE in China over 2005-2011?

**Highlights:**
- High impact and high stakes: university and career path.
- 80% of students had justified envy prior to policy reform.
  - On average, a student justifiably envies 357 students.
- Policy showed improvement (~60%), especially with lower socioeconomic background students.
  
**Comments:**
- The impact on average (or minimum) CEE scores at university level.
- Retention, stability.
  - Retaking: due to desire to improve their placement towards a higher ranked university, or are there other dimensions? E.g., location, major.. Evidence from survey data?
- College graduation rates, GPA? High school test taking skills vs. college performance.

---
**Comments (cont.):**
- STEM, non-STEM heterogeneity results? Are the effects STEM driven?
- Figure 5, 2005-2011: Does the hump shape remain if observations are <br> broken down by each year?
- More background info on university rankings: E.g., are rankings determined by the minimum cutoff?
- Are there schools that moved up (or down) the rankings over the sample period? Do students respond to a ranking change in the way your simulation predicts?
- A brief few sentences on why Immediate Acceptance was the main algorithm?
- Big picture: better school matches --> better labor market outcomes?

Survey ideas:
- Student preferences data from the Ministry of Education? Possibility of surveying students for their preferences?
  - Even through an anecdotal sample, showing correlation with actual university rankings at the province level.
- "Are you satisfied with your placement?"
- "Were you overly cautious in your selections?" 
- Typo: Page 27, line 3. Equation number: "??".
